\Large Plotting the Single-Electron Solution to Schr\"{o}dinger's Equation with OpenCL

### 2010-05-07 paper/paper.tex
Update plots, write more words

\section{Introduction}

asdfasdfadsf asdf adsf asdf asdf adfasdf adsf adf asfd

asdfasdfadsf asdf adsf asdf asdf adfasdf adsf adf asfd

asdfasdfadsf asdf adsf asdf asdf adfasdf adsf adf asfd

asdfasdfadsf asdf adsf asdf asdf adfasdf adsf adf asfd

@@

@@

Also, $\psi$ depends on two external functions: $Y$, the spherical harmonic equation (equation \ref{yFunc}), and $L$, the Laguerre polynomial (equation \ref{laguerre}).

@@

The overhead incurred during this copy can be seen in the chart in figure \ref{fig:overheadPlot} to be negligible --- in the range of a ten-thousandth of a percent of the total runtime when working on the GPU, and a one-hundred-thousandth of a percent when working on the CPU, where the data has a shorter distance to travel.

@@

One oft-cited measure of the performance of a computational device is its {\it performance-per-dollar}; this is especially of interest for consumers with budgets or people building large computation clusters. In order to measure performance-per-dollar, we have to define {\it performance} in the context of our problem. In all of the plots in this section, performance is measured as the number of samples per second. Figures \ref{fig:costEffectiveness}, \ref{fig:transistorPlot}, and \ref{fig:wattPlot} all use a 500$\times$500 image, with 2000 samples per pixel, for $500,000,000$ total samples.

@@

Section \ref{cameraTransformation} covered the ideal solution to the problem of comprehending the shape of the orbital from our 2D representation --- however, if that solution proved to be too challenging, one could instead generate an animation of slices through the cloud, each slice being similar to figure \ref{fig:slice}. This would provide another form of interesting visualization of the resulting data.

@@

>>>>

@@

This is the fundamental formula involved in our computation --- it is this equation which we evaluate at each sample. The result of this equation gives the probability that the single electron of our hydrogen atom is at the particular chosen location in the spherical coordinate system, $\left(\theta, \phi, r\right)$, which is the information that we eventually aim to plot.

@@

Also, $\psi$ depends on two external functions: $Y$, the spherical harmonic equation (equation \ref{yFunc}), and $L$, the Laguerre polynomial (equation \ref{laguerre}), which will be detailed in sections \ref{sphericalHarmonics} and \ref{laguerreLegendre}, respectively.

@@

The overhead incurred during this copy can be seen in the chart in figure \ref{fig:overheadPlot} to be negligible --- in the range of a tenth of a percent of the total runtime when working on the GPU, and a one-hundred-thousandth of a percent when working on the CPU, where the data has a shorter distance to travel.

@@

One oft-cited measure of the performance of a computational device is its {\it performance-per-dollar}; this is especially of interest for consumers with budgets or people building large computation clusters. In order to measure performance-per-dollar, we have to define {\it performance} in the context of our problem. In all of the plots in this section, performance is measured as the number of samples per second. Figures \ref{fig:costEffectiveness} and \ref{fig:wattPlot} all use a 500$\times$500 image, with 2000 samples per pixel, for $500,000,000$ total samples.

@@

Section \ref{cameraTransformation} covered the ideal solution to the problem of comprehending the shape of the orbital from our 2D representation --- however, if that solution proved to be too challenging, one could instead generate an animation of slices through the cloud, each slice being similar to figure \ref{fig:slice}. This would provide another form of interesting visualization of the resulting data, rather similar to the data collected by an MRI device.

\subsection{Automatic Scaling}

Our OpenCL kernel currently contains an arbitrary zoom factor which needs to be adjusted based on the orbital configuration --- higher energy electron states lead to larger probability clouds. Automatically generating this zoom factor would lead to significantly improved ease of use when changing between different configurations. This could most effectively be implemented by finding a formula for a reasonable scale factor given a set of $n, l, m$ values.

@@

After consuming many computer-hours computing the 3-2-0 orbital repeatedly, I've come to a few clear conclusions. Firstly, scientific computation --- the calculation of atomic orbitals, at the very least --- should clearly be a prime target for
